---
title: "Project_Data_Anlytics"
author: "Bron_Luca, Grandadam_Patrik"
date: "26 10 2018"
output: html_document
---

```{r}
cred <- read.csv2("GermanCredit.csv")
cred <- data.frame(cred)
```


```{r}
nrows<-nrow(cred)
n.missing<-rowSums(is.na(cred))
sum(n.missing)
```

We then have to be sure that we have no wrong recorded data (for instance, a duration of 1 Billion). To be sure that we have no outlier that results from a human error, we can inspect each variable with a summary to see if everything seems correct.
As an example, we can appreciate the summary of the variable *"HISTORY"*.

```{r}
summary(cred$HISTORY)
```

However, doing this for all variables can be long and boring. It can be better to represent these number visually with a boxplot. With this representation, we can see at a glance if some values might be "dirty".



```{r, fig.height=3, fig.width=3, warning=FALSE}

for (i in 1:32){
  if(range(cred[,i]<=5)){
    barplot(table(cred[,i]), main=colnames(cred[i]), xlab="")
    } else
    {boxplot(cred[,i], main=colnames(cred[i]))}
  }
```

```{r, fig.height=3, fig.width=3, warning=FALSE}
for (i in 1:32){
  if(range(cred[,i]<10)){
    print(summary(cred[,i]))
    } else
    {boxplot(cred[,i], main=colnames(cred[i]))}
  }
```


Pb with education ; guarantor











