---
title: "Project_Data_Anlytics"
author: "Bron_Luca, Grandadam_Patrik"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

 - [Introduction](#Intro)
 - [Exploratory analysis](#Exp)
 - [Modelling](#Mod)
    - [CART](#CART)
    - [Logistic Regression](#Logit)
    - [....]()
    - [....]()
    - [....]()
 - [Cross Validation Approach](#CV)
 - [...](#)
 - [...](#)

**LE CODE EN COMMENTAIRE, C'EST JUSTE POUR POUVOIR KNIT PLUS VITE!!** (avec cache = TRUE, ca re-run pas le code, mais le markdown doit quand meme compiler les graphes, du coup ca prend du temps à chq fois...)


```{r include = FALSE}
knitr::opts_chunk$set(echo=TRUE)
```


```{r, message=FALSE, echo=FALSE}
cred <- read.csv2("GermanCredit.csv")
cred <- data.frame(cred)
attach(cred)
```


```{r, message=FALSE, echo=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(stringr)
library(DataExplorer)
library(corrr)
library(rpart)
library(rpart.plot)
library(maptree)
library(caret)
library(gmodels)
library(MASS)
library(nnet)
library(neuralnet)
library(NeuralNetTools)
library(kknn)
```


```{r, echo=FALSE}
my_theme <- function(base_size = 10, base_family = "sans"){
  theme_minimal(base_size = base_size, base_family = base_family) +
    theme(
      axis.text = element_text(size = 10),
      axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
      axis.title = element_text(size = 12),
      plot.title = element_text(hjust = 0.5),
      panel.grid.major = element_line(color = "grey"),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "aliceblue"),
      strip.background = element_rect(fill = "lightgrey", color = "grey", size = 1),
      strip.text = element_text(face = "bold", size = 10, color = "black"),
      legend.position = "bottom",
      legend.justification = "top", 
      legend.box = "horizontal",
      legend.box.background = element_rect(colour = "grey50"),
      legend.background = element_blank(),
      panel.border = element_rect(color = "grey", fill = NA, size = 0.5)
    )
}
```

```{r}
names(cred) <- tolower(names(cred)) # changing the name of the variable into lowercase
cred <- cred[,-1] # deleting the first useless column
```


```{r, results='hide'}
sum(is.na(cred)) # checking if we have missing data
```

# Introduction {#Intro}

Parler de:
- méthode utilisée
- grandes étapes
- classification task (goal) =/= prediction
- [à compléter...]

--> Exploration des données = 1st insight
--> Modelling: train/set set + selection du "meilleur" arbre(pruning)/svm(tuning)/NNET(nb of layers)/regression logicstic/K-NN(choisir K)/etc. + presentation de détail de tout ce bordel
--> Cross validation avec les meilleurs de chq models pour selectionner le grand gagnant...

--> Description des variables (comme ca c'est plus simple de s'en sortir?!)


## Exploratory analysis 

### Explanatory variables

#### Overview 

Before beginning any kind of analysis, we have to understand the data we are working with. 

```{r}
data.frame(variable = names(cred),
           classe = sapply(cred, typeof),
           first_values = sapply(cred, function(x) paste0(head(x),  collapse = ", ")),
           row.names = NULL) %>% 
  kable(caption="Overview of our data") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(1, width = "10em", border_right = T) %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "18em") %>%
  scroll_box(width = "70%", height = "200px")
  
```


&nbsp;

As we can see, the data are coherent with the infos that "the client" provided us. Most of them are binary of categorical, while only few are numerical.  

More than seeing the first values of our variables and their types, we also need to understand how distributed they are and their link with each other. Thanks to a correlation plot, we can see the correlation between each pair of variable, but especially their correlation with our response variable in which we are interested in.  
We see for instances that variables like *chk_acct*, *duration*, *history*, *sav_accnt* or *rent* are highly correlated (positively or negatively) with our outcome variable and that they will be likeli to influe it in the models that we are going to plot. Others like *present_resident* or *retaining* should have low impact.  

```{r}
plot_correlation(cred, type="all", title = "correlation graph")
```



In addition, we can appreciate the summary of the different variables. The frequency table of *history* is presented below as an example:  

```{r, echo=FALSE}
c(summary(cred$history)) %>% as.data.frame %>%
  kable(caption = "Summary of variable history", align = "l", col.names = c("Value")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "float_left"
  )

table(cred$history) %>% kable(caption = "Frequency table of history",
                              col.names = c("Values", "Frequency")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F
  )
```


&nbsp;  
&nbsp;  

However, presenting such a summary for all variables can be long and boring. It can be better to represent these number visually. A Boxplot is optimal to get all the important values for the numerical data, while a barplot will give us strong insights for categorical data. Let's appreciate the following graphs:  

```{r, fig.height=3, fig.width=3, warning=FALSE, cache=TRUE}

# for (i in 1:(length(cred)-1)) {
#   if (range(cred[, i] < 5)) {
#     print(
#       ggplot(cred, aes(x = cred[, i])) + geom_bar(stat = "count", position = "dodge") +
#         ggtitle(str_c("Barplot of\n", paste(
#           colnames(cred[i])
#         ))) +
#         xlab(colnames(cred[i])) +
#         ylab("Total") +
#         my_theme()
#     )
#   } else
#   {
#     print(
#       ggplot(cred, aes(y = cred[, i])) + geom_boxplot() + 
#         ylab(colnames(cred[i])) +
#       ggtitle(str_c("Boxplot of\n ", paste(
#         colnames(cred[i])
#       ))) +
#         my_theme() +
#         theme(
#         axis.text.x=element_blank())
#     )
#   }
# }

```

Thanks to these graphs, we can better understand our data at a glance and will be able to refer to them when needed.  

In addition, these graphs enable un too see that some data are not tidy. For instance, *education* should be a binary variable. However, we can see on the histogram of this variable that we have data where $-1$ were recorded. We have the same problem for the binary variable *guarantor* were a value $2$ is present.  
In addition, we can also have strong suspitions that the variable *age* has wrong recorded data as we can see an outlier with a value much bigger than 100.  
We will have to confirm our first assumptions and to modify these dirty data in an appropriate way.  

#### Problematic variables

##### *Age* 

Let's first look at our variable *age*. We assume that, generally, a person will never live more than a hundred year, and will never contract a credit at such ages. This is why the data with $Age > 100$ are definitely wrong recorded. We will therefore have to replace them in our database.  
First, we have to find how much data are potentially dirty according to our assumptions and to localisate them in order to replace them.  

```{r, echo=FALSE}
attach(cred)
```


```{r, echo=FALSE}
table(age>=100) %>% kable(caption="Number of instances with age > 100") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "float_left") %>%
  column_spec(1, width = "5em", border_right = T) %>%
  column_spec(2, width = "5em")
which(age>100) %>% kable(caption="Position of instance with age > 100") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  column_spec(1, width = "9.5em") 
```

&nbsp;  
&nbsp;  


According to our results, we have one data with $age > 100$ that has to be replaced. It is the instance `r which(age>100) ` and its value is `r age[which(age>100)]`.  

We can consider different options to replace this value. The first one could be to replace it by a value at random within the range (a value at random between `r min(age)`  and `r max(age[age!=max(age)])`, which is the second lowest value after $125$.  
However, according to the following histogram, the distribution of the age (without the erroneous data) is inequal with a concentration around small values (which is logical as young people generally have less money than elders and therefore are more subject to ask for credits).  

```{r, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cred, aes(x = cred$age)) + 
  geom_bar(stat = "count", position = "dodge") +
  ggtitle(str_c("Barplot of age without the erroneous data")) +
  xlab("Age") +
  ylab("Frequency") +
  xlim(c(min(age),max(age[age!=max(cred$age)]))) +
  my_theme()
```

It could therefore be possible to replace it at random with different probabilities according to the size of each class.  
We prefer to opt for the median (equal to `r median(age[age!=max(age)])`) to replace our problematic value as it offers more convenience.  
Note that for calculating the median, our problematic value should not be used.  

```{r}
cred$age[which(age>75)] <- median(age[age!=max(age)])
```

An alternative could have been to use the mean, but, as we have no really big outlier, both values would have been close to eachother ($mean = `r mean(age)`$ while $median = `r median(age)`$).  


Next, we also have to deal with our two categorical data that have been wrong recorded:  
    - one in *education*  
    - one in *guarantor*

They also have to be cleaned. 

##### *Education*

The following is again the barplot of *education*. 

```{r, fig.height=4, fig.width=4, echo=FALSE}
ggplot(cred, aes(x = cred$education)) +
  geom_bar(stat = "count", position = "dodge") +
  ggtitle(str_c("Barplot of education")) +
  xlab("Education") +
  ylab("Count") +
  my_theme()
```

Here, the likelihood that this wrong recorded data is equal to $0$ is clearly higher. Therefore, each of the previously presented methods (using the mean, using the median and even assigning it to a class at random) would with a high probability result in assigning this instance and assign it the value $Education = 0$.  
We can confirm these first assumption with a frequency table:  

```{r, echo=FALSE}
edu <- rbind(table(education), paste(round(prop.table(table(education)) * 100, 1), "%"))
rownames(edu) <- c("sample size", "proportion")
edu %>% kable(caption = "Frequency table of education", align = 'c') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(1, border_right = T)
```


&nbsp;

It is indeed more appropriate to replace our value by 0 as the probability of belonging to this class is close to 20 times bigger.  

```{r}
cred$education[which(education==-1)] <- 0
```

&nbsp;  

##### *Guarantor*

Concerning the variable *guarantor*, we can look at the frequency table and plot the barplot as well:  

```{r, echo=FALSE}
gua <- rbind(table(guarantor), paste(round(prop.table(table(guarantor)) * 100, 1), "%"))
rownames(gua) <- c("sample size", "proportion")
gua %>% kable(caption = "Frequency table of guarantor", align = 'c') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "float_left") %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, width="5em") %>%
  column_spec(3, width="5em") 
```


```{r, fig.height=3, fig.width=3, echo=FALSE}
ggplot(cred, aes(x = cred$guarantor)) +
  geom_bar(stat = "count", position = "dodge") +
  ggtitle(str_c("Barplot of guarantor")) +
  xlab("Guarantor") +
  ylab("Count") +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  my_theme()
```

Again, for the same reasons, it is preferable to replace the wrong recorded data by 0.  

```{r}
cred$guarantor[which(guarantor==2)] <- 0
```

##### *present_resident*

In addition, the variable *present_resident* is also problematic as it doesn't have the same range as the other categorical values. Its range goes from `r min(range(present_resident))` to `r max(range(present_resident))` whereas it should go from 0 to 3 like the other ones. We can modifiy its values in order to have the same format everywhere.
 
```{r}
cred$present_resident <- cred$present_resident - 1
```
 
 
**Variable num_credits: y'a pas de 0, pas cohérent...**
 
These first steps have enabled us to better understand our explanatory variables and to clean the problematic ones.  
We now have to focus in detail to the response variable on which the predictions should be made.   
 
### Response variable

As our final goal is to predict if a customer should be classified as a risky one or not, we have to have a particular look at our response variable that establishes if an applicant presents a good or a bad risk.  

```{r, echo=FALSE}
cred$response <- as.factor(ifelse(cred$response==1, "good", "bad")) # tranform it as a factor
ggplot(cred, aes(x = cred$response)) + geom_bar(stat = "count", position = "dodge") +
  ggtitle(str_c("Barplot of the response variable")) +
  xlab("Response variable") +
  ylab("Total") +
  my_theme()
```

```{r, echo=FALSE}
res <- rbind(table(response), paste(round(prop.table(table(response)) * 100, 1), "%"))
rownames(res) <- c("sample size", "proportion")
res %>% kable(caption = "Frequency table of our response variable", align = 'c') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F) %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, width="5em") %>%
  column_spec(3, width="5em") 
```

As we can see, if a random customer steps in the bank, the *a priori* probability that he will present a good ranking will be of 70%.  
Without any calculations, the bank has more chances to make a good decision when octroying a credit.  
However, the consequences can be really dramatic if 30% of the credits that the bank gives are not totally reimbursed. That's why we have to develop a model that will have an accuracy much better than these initial 70% that are obtained using a naive method of always octroying a credit.  

We will get to this later. First, after having presented each variable, it could be interesting to see if we can already have some assumptions concerning the relations between the expanatory variables and the response variable.

### Interactions between the explanatory variables and the response variable


Text... 
 
```{r, fig.width=3, fig.height=3, cache=TRUE, echo=FALSE}

for(i in 1:(length(cred) - 1)){
  print(
    ggplot(cred, aes(
      x = response, y = cred[, i] ,  group = response
    )) +
      geom_boxplot() +
      xlab("Response variable") +
      ylab(colnames(cred[i])) +
      ggtitle(str_c(
        "Interaction between\n ",
        paste(colnames(cred[i]), "and the\n response variable")
      )) +
      my_theme()
  )
}

```

--> Expliquer qu'on peut deja avoir un premier apriori sur les variables qui vont avoir un impact






# Modelling {#Mod}

Before beginning to work on our different models, we can create a test set and a training set in order to build the models. This procedure is used is order to avoid overfitting and to predict instances which have been used while building the model. 
In order to evalate the performance of the different models, we will have to use the exact **same training and test sets** for each model to be sure that the performance differences will result from the model we use and not from the randomess of splitting differently both sets.   
A Cross-Validation will be performed at the end in order to compare the different models and to choose which one should be used to make good predictions.  

```{r}
set.seed(12345) 
index.train <- sample(1:nrow(cred), size=nrow(cred)*0.7, replace=FALSE)
cred.train <- cred[index.train,]
cred.test <- cred[-index.train,]
```

To evaluate our models, we will use the accuracy as main measure of performance. However, computing the accuracy for each model can be quite long... We prefer to build a function to be able to retrieve at any time based on a confusion matrix:  

```{r}
# Creating of a function to retrieve the accuracy from a confusion matrix
accuracy <- function(c){
  print(sum(diag(c))/sum(c))
}
```



## CART {#CART}

** Petite description de CART, ...**
--> Comment c'est calculé (decrease of impurity criterion)
--> iterative procedure etc.

### Building the model


```{r}
cart.model <- rpart(response ~ .,  data = cred.train, method = "class")
```


```{r}
rpart.plot(cart.model, main="Original decision tree")
```

--> At this time, we have obtained a decision tree with good prediction capabilities, but that is also really complex (a lot of split and of branches). An idea to simplify this model without loosing too much predictive capabilities, it could be useful to prune it, keeping only the most important splits linked to the most important variables.

### Tuning the model: Pruning

As already said, our complex tree has to be pruned in order reduce its complexity. To do so, we will use the *1 - SE rule*.   
The idea of this rule is really general. As one would establish a t-test in statistics to see if two measures are *statistically different*, the 1 - SE rule tries to establish if two models produce statistically different results (if we can affirm that one outperforms the other).  
We therefore consider the *xerror* (the criterion in which we are interested in and that we want to minimize) and its standard deviation *xstd*. A models that falls within 1 standard deviation of the most complex model can be considered as equivalent in term of performance. Therefore, using this rule, we will be able to prune the tree to get a much simplier model, without loosing in quality as the performance capability of our new model will be *statistically the same* as the first one.  
To select the size of our pruned tree, we will look at the xerror of our original tree (the most complex one) and add one standard error *xstd*. We will then select the simplier tree with an xerror that lies within the calculated value.

Let's have a look at these values from our original tree and decide where to prune it.

```{r, echo=FALSE, fig.height=5, fig.width=5}
cart.model$cptable %>% 
  kable(caption = "CP table of the CART model") %>% 
  kable_styling(
  bootstrap_options = c("striped", "hover", "condensed"),
  full_width = F, 
  position = "float_left"
)
head(cart.model$variable.importance, n = 6) %>%
  kable(caption = "Variable importance table first 6 instances") %>% 
  kable_styling(
  bootstrap_options = c("striped", "hover", "condensed"),
  full_width = F
) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em")

plotcp(cart.model)
```


```{r, echo=FALSE}
min.xstd <- cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable)] # xstd associated with lowest xerror
min.xerror <- cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable) - 1] # lowest xerror
sum.xe.xstd <- min.xstd + min.xerror # sum of both
cp.pruned <- cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),1]# CP value to which to prune the tree ; min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd)) representing the row to be pruned at
```
 
Accoring to our first table, the minimal *xerror* is equal to `r cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable) - 1]` , the minimal *xstd* to `r cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable)]` and the sum of both is therefore equal to `r sum.xe.xstd`.  

The highest xerror below this value is equal to `r cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),4]` and we will therefore prune the tree at CP = `r cp.pruned`. According to our previous table, this represents `r cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),2]  ` splits to be kept, equivalent to a tree of size `r cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),2] + 1  `.  
It is also possible to observe this value on the graph where the dash line indicates the *xerror* plus its *xstd* from the most complex tree. We therefore select the less complex tree under this line, which is the size of size `r cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),2] + 1  ` (or, again, with `r cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < sum.xe.xstd))),2]  ` splits).  

We thus prune the tree at this value (the *R* function requires to indicate CP.)

```{r}
cart.pruned <- prune(cart.model, cp=cp.pruned)
```


```{r, echo=FALSE}
rpart.plot(cart.pruned, main="Pruned decision tree")
```

We can visualize this new pruned tree that is much smaller and therefore less complex than our original one and will use it to do our predictions, to build the confusion matrix and to calculate the underlying accuracy.  

### Predicting the values of the testing set

```{r, comment=NA}
pred.cart <- predict(cart.pruned, newdata = cred.test, type = "class")
cart.tab <- table(Predictions = pred.cart, Observations = cred.test$response) # confusion matrix.
cart.tab %>% kable(caption = "Confusion matrix for the CART model",
                   col.names = c("Predict bad", "Predict good")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "l") %>%
  column_spec(1, border_right = T, width = "5em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em")

```

Based on this table, we can calculate the accuracy using our previously build function, and that calculates the element weel classified divided by the total number of elements.  

```{r}
# accuracy using our previously build function
accuracy(cart.tab) 
```

It is possible to have more informaion, with for instance the sum of each rows with the following cross table.

```{r comment=NA, echo=FALSE, fig.height=3, fig.width=3}
CrossTable(x = cred.test$response, y = pred.cart, prop.chisq = FALSE)
```

We can see that `r cart.tab[1,1] + cart.tab[2,1]` are predicated as bad and `r cart.tab[1,2] + cart.tab[2,2]` are predicted as good. 


--> Parler de accuracy en elle meme (0.74 pas top par rapport aux 0.7 de base si on prédit que "good")
--> Parler des bonnes predictions de 0 (c'est elles qui nous intéressent et prédire que 1 conduirait la banque à faire faillite)
--> Parler **FALSE POSTIVIE** / FALSE NEGATIVE / TRUE POSITIVE / TRUE NEGATIVE







## Logistic regression {#Logit}

--> Parler de pourquoi Logistic regression (fait un bon taf quand outcome binaire)



### Building the model

```{r comment=NA}
logit.model <- glm(response ~., data=cred.train, family="binomial")
summary(logit.model)
```

--> Parler du fait qu'on a des similitudes avec CART (les variables importantes avant ont aussi des coeffs signi ici... ** pas toutes... ** --> nuancer...).
--> Parler du fait qu'on a aussi plein de variables inutiles et qu'on va faire une stepwise pour minimiser AIC 
--> Dire l'idée de AIC (arbritrage entre perf du model et complexité)
--> Expliquer comment ca marche

### Tuning the model: Stepwise selection according to AIC criteria


```{r, results='hide', echo=TRUE}
logit.step <- step(logit.model, direction="both")
summary(logit.step)
```


--> Parler du fait qu'on a quand meme encore énormément de variables mais que le AIC est minimisé
--> Parler du fait qu'on pourrait en virer manuellement (mais long et chiant et pas forcément utile)

### Predicting the values of the testing set


```{r}
pred.logit.step <- ifelse(
  predict(logit.step, newdata=cred.test, type="response") > 0.5, "good", "bad"
  ) # the predictions of the class
pred.logit.step.prob <- predict(logit.step, newdata=cred.test, type="response")

data.frame(pred.logit.step.prob,cred.test$response) %>% 
  ggplot(aes(x=cred.test$response, y = pred.logit.step.prob, group=cred.test$response)) + geom_boxplot() +
        my_theme() +
  ggtitle("Predicted probabilities against real values") +
  xlab("Values of the testing set") +
  ylab("Predicted probabilities of the logistic regression") 
```

```{r}
glm.tab <-
  table( Observations = cred.test$response, Predictions = pred.logit.step) # confusion matrix.
glm.tab %>% kable(caption = "Confusion matrix for the Logistic regression model",
                  col.names = c("Predict 0", "Predict 1")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "l"
  ) %>%
  column_spec(1, border_right = T, width = "5em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em")

accuracy(glm.tab) # accuracy
```



FALSE POSITIVE: 47 sur les 250 sont prédits 1 alors qu'ils sont 0... C'est la merde
Idée: on peut changer la proba limite pour dire que c'est "bon" pour avoir moins de FALSE POSITIVE...
Ca va baisser l'accuracy, mais ca va potentiellement nous faire perdre moins d'argent (on va refuser plus souvent les crédits à risques, et aussi les crédits sans risques...)


```{r}
pred.logit_0.7 <- ifelse(
  predict(logit.step, newdata=cred[-index.train,], type="response") > 0.75, "good", "bad"
  ) # the predictions of the class
```

```{r}
glm.tab <-
  table(Observations = cred.test$response, Predictions = pred.logit_0.7) # confusion matrix.
glm.tab %>% kable(caption = "Confusion matrix for the adapted Logistic regression model",
                  col.names = c("Predict bad", "Predict good")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "l"
  ) %>%
  column_spec(1, border_right = T, width = "5em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em")

sum(diag(glm.tab))/sum(glm.tab) # accuracy
```

--> En passant la limite à 0.75, on a gardé une bonne accuracy, et on fait moins d'erreurs d'évaluation parmis les "risky". Faut voir se que la banque peut se permettre comme marge et si les risky conduisent forcément à des pertes...


## Neural Network 

### Building the model and optimizing it: selecting the number of neurones in the hidden layer

La "littérature" (https://stats.stackexchange.com/questions/181/how-to-choose-the-number-of-hidden-layers-and-nodes-in-a-feedforward-neural-netw) suggère de garder 1 seul layer un nb de neuronnes entre 1 et le nbr de dim: on va les tester tous et garder le meilleur...
"In sum, for most problems, one could probably get decent performance (even without a second optimization step) by setting the hidden layer configuration using just two rules: (i) number of hidden layers equals one; and (ii) the number of neurons in that layer is the mean of the neurons in the input and output layers."

"Over-parametrization quickly lead to instability in the estimate and can lead to overfitting. One possibility is to impose a penalty on the largest weights during the optimization. This is called regularization and, more specifically in the context of neural network, weight **decay.**"

--> On essaye de trouver le nombre "optimal" de neurones. Vu que neural network utilise des valeurs aléatoires au début pour lancer l'algo etc. Ca varie. On calcule donc 10 fois l'accuracy liée à chaque nombre de neurones et voir si y'a un nb de neurones optimal.

**UTILISER A CHAQUE ITERATION DES TRAIN ET DES TESTS SETS DIFFERENTS** !

```{r, cache=TRUE, results='hide'}

acc.nnet.cv <- matrix(nrow=30,ncol=10) 
for (j in 1:10){
index.train1 <- sample(1:nrow(cred), size=nrow(cred)*0.7, replace=FALSE)
cred.train1 <- cred[index.train1,]
cred.test1 <- cred[-index.train1,]
nnet.model = list()
for (i in 11:30) {
  nnet.model[[i]] = nnet(cred.train$response~., data = cred.train, size=i, maxit=200, decay = 1)
}
pred.nnet=list()
for (i in 11:30){
  pred.nnet[i] <- predict(nnet.model[i], cred.test, type="class")
  
}# making the predictions
  tab.nnet=list()
for (i in 11:30){
  tab.nnet[[i]] <- table(Reality=cred.test$response, Predicted=unlist(pred.nnet[i]))
}
  acc.nnet = list()
for (i in 11:30) {
  acc.nnet[i] <-
    sum(ifelse(cred.test$response == unlist(pred.nnet[i]), 1, 0), na.rm = TRUE) /
    length(cred.test$response)

  acc.nnet.cv[i,j] <- acc.nnet[[i]]} 
}

```

On utilise à chaque itération des train et test sets différents.

```{r}
mean.acc.nnet.cv <- numeric(30)
sd.acc.nnet.cv <- numeric(30)
for(i in 11:30){mean.acc.nnet.cv[i] <- mean(acc.nnet.cv[i,])
sd.acc.nnet.cv[i] <- sd(acc.nnet.cv[i,])}
mean.acc.nnet.cv[-c(1:10)] # average mean for the models with i = 11,..,30 nodes
accu <- data.frame(Average=mean.acc.nnet.cv[-c(1:10)], Neurones = c(11:30))
```

The 

```{r, comment=NA}
which.max(mean.acc.nnet.cv) # neurones leading to the model with the highest accuracy
mean.acc.nnet.cv[which.max(mean.acc.nnet.cv)] # the accuracy
```

The maximum accuracy  is equal to `r mean.acc.nnet.cv[which.max(mean.acc.nnet.cv)]`.  
On the following plot, we can see at a glance the accuracies and the model that we are going to select.

```{r, echo=FALSE}
accu %>% ggplot() +
  geom_point(aes(x = Neurones, y = Average)) +
  geom_hline(yintercept = mean.acc.nnet.cv[which.max(mean.acc.nnet.cv)], col =
               'red') +
  scale_x_continuous(breaks = c(11:30)) + scale_y_continuous(breaks = round(c(
    seq(min(mean.acc.nnet.cv[mean.acc.nnet.cv != 0]), max(mean.acc.nnet.cv),
    by = (max(mean.acc.nnet.cv) - min(mean.acc.nnet.cv[mean.acc.nnet.cv != 0]))/4
  )),3)) + ylab("Average accuracy") + ggtitle("Average accuracy according to the number of neurones in our network") + my_theme()
```

We can directly see which that the model with `r which.max(mean.acc.nnet.cv)` neurones presents the highest accuracy.

Obviously, this choice is subject to discussion and other methods could be preferred. At the end, the differences resulting from the use of our different models are really low, meaning that they have all quite similar predictive capabilities. 

We can therefore continue to explore further the model with `r which.max(mean.acc.nnet.cv)` neurones that we retained. 

#### TESTING DIFFERENT DECAYS

Note, on a considéré plus de decay, mais pour plus de "computational efficicency", on va en display seulement certains...

```{r, cache = TRUE, results='hide'}
acc.nnet.cv2 <- matrix(nrow=length(seq(2^-8,2,2^-3)),ncol=10) # we considered initially extreme small values like seq(0,2^-5,2^-8), seq(0,2^-4,2^-10) intermediate and high and the range that we propose here best fits the data.
j <- 1
for (j in 1:10){
index.train2 <- sample(1:nrow(cred), size=nrow(cred)*0.7, replace=FALSE)
cred.train2 <- cred[index.train2,]
cred.test2 <- cred[-index.train2,]
nnet.model2 = list()
pred.nnet2=list()
tab.nnet2=list()
acc.nnet2 = list()
k <- 1
for (i in seq(2^-8,2,2^-3)) {
  nnet.model2[[k]] = nnet(cred.train$response~., data = cred.train, size=which.max(mean.acc.nnet.cv), maxit=200, decay = i)
pred.nnet2[[k]] <- predict(nnet.model2[k], cred.test, type="class") #  making the predictions
tab.nnet2[[k]] <- table(Reality=cred.test$response, Predicted=unlist(pred.nnet2[k]))
acc.nnet2[[k]] <- sum(ifelse(cred.test$response == unlist(pred.nnet2[k]), 1, 0), na.rm = TRUE) /
    length(cred.test$response)
  acc.nnet.cv2[k,j] <- acc.nnet2[[k]]
  k <- k+1
  } 
  j <- j+1
}
```


```{r}
mean.acc.nnet.cv2 <- numeric(16)
sd.acc.nnet.cv2 <- numeric(16)
for(i in 1:16){mean.acc.nnet.cv2[i] <- mean(acc.nnet.cv2[i,])
sd.acc.nnet.cv2[i] <- sd(acc.nnet.cv2[i,])}
mean.acc.nnet.cv2 # average mean for the models with i = 11,..,30 nodes
accu2 <- data.frame(Average=mean.acc.nnet.cv2, Decay = seq(2^-8,2,2^-3))
```


```{r, comment=NA}
which.max(mean.acc.nnet.cv2) # neurones leading to the model with the highest accuracy
mean.acc.nnet.cv2[which.max(mean.acc.nnet.cv2)] # the accuracy
round(seq(2^-8,2,2^-3)[which.max(mean.acc.nnet.cv2)],1) # the retained decay
```

### Model selection and predicting the values of the testing set

We present you the characteristics of the model retained, with `r which.max(mean.acc.nnet.cv)` neurones in the hidden layer and a decay of `r round(seq(2^-8,2,2^-3)[which.max(mean.acc.nnet.cv2)],1)`.
As usual, we trained the model and predict the values of the test set to be able to build the confusion matrix and to calculate the accuracy. 

```{r, results='hide'}

nnet.model.retained <- nnet(cred.train$response ~ .,data = cred.train,maxit = 200,size = which.max(mean.acc.nnet.cv), decay = round(seq(2^-8,2,2^-3)[which.max(mean.acc.nnet.cv2)],1))

pred.nnet.retained <- predict(nnet.model.retained, cred.test, type="class") # predictions on the test set


tab.nnet.retained <- table(Reality = cred.test$response, Predicted = unlist(pred.nnet.retained)) # confusion matrix

acc.nnet.retained <- sum(ifelse(cred.test$response == unlist(pred.nnet.retained), 1, 0), na.rm = TRUE) /
  length(cred.test$response) # accuracy
```

In addition, we can plot our neural network:

```{r, comment = NA, fig.width=10, fig.height=10, echo=FALSE}

# plot
plotnet(nnet.model.retained, alpha_val=0.1,
        circle_col="steelblue1", pos_col="blue", neg_col="red", bord_col="black", pad_x=0.8)
```

This graph shows that our model can be quite complex, there a plenty of arrows. It is not necessary to understand precisely all of them and they can be seen as a "black box", meaning that the interpretability of such a model is modest. But, afterall, what we need is to make good predictions!


```{r, echo=FALSE}
# confusion matrix
tab.nnet.retained %>% kable(caption = "Confusion matrix of the fitted NNET model",
                                          col.names = c("Predict good", "Predict bad")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "l"
  ) %>%
  column_spec(1, border_right = T, width = "5em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em")
```

We obtain a final accuracy of `r round(acc.nnet.retained,3) ` on our testing set.


















## Support Vector Machine (SVM)

### Building the model

### Optimizing the model: selecting good cost and gamma parameters

### Predicting the values of the testing set


## Model x (K-nn)

### Building the model

```{r}
scaled.cred <- scale(cred[,-length(cred)]) %>% data.frame(response=cred$response)
# scaling except last row (except response)

scaled.cred.train <- scale(cred.train[,-length(cred.train)]) %>% data.frame(response=cred.train$response)
scaled.cred.test <- scale(cred.test[,-length(cred.test)]) %>% data.frame(response=cred.test$response)
```

```{r}
# Creation of 20 KNN: 10 with i={1,..,10} and k = 2 and 10 with i={1,..,10} and k = 3 
knn.model = list()
k <- 0
for (j in 2:3) {
  for (i in 1:20) {
    knn.model[[20 * k + i]] <- kknn(response ~ ., k=i, distance=j,train=scaled.cred.train, test=scaled.cred.test)
  }
  k <- k+1
}

# making the predictions on the testing set
pred.knn=list()
for (i in 1:length(knn.model)){
  pred.knn[[i]] = table(Prediction=knn.model[[i]]$fitted.value, Actual=cred.test$response)
}

# calculating the accuracy
acc.knn = list()
for (i in 1:length(knn.model)) {
  acc.knn[i] <- sum(diag(pred.knn[[i]]))/250
}
```

```{r, comment=NA, echo=FALSE}
selected.knn <- knn.model[[which.max(acc.knn)]] # selected knn
paste("The selected knn model uses a distance of", selected.knn$distance) %>% paste("and is computed with the", ifelse(which.max(acc.knn)<20,which.max(acc.knn),which.max(acc.knn)-20)) %>% paste("neerest neighbors.") %>%
paste("The obtained accuracy is equal to", acc.knn[[which.max(acc.knn)]]) 

# confusion matrix
pred.knn[which.max(acc.knn)] %>% kable(caption = "Confusion matrix of the fitted KNN model",
                                          col.names = c("Predict good", "Predict bad")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F,
    position = "l"
  ) 


```



Petit DB donc pas un pb que "lazy learner"




### Optimizing the model: selecting the number of nodes and layers

### Predicting the values of the testing set

Apres y'en a marre...






















# Cross Validation approach {#CV}

--> Expliquer pourquoi on fait une cross-validation
--> 



Creation of 10 different sets in order to do the Cross-Validation.
The number of instances being `r nrow(cred)`, we will make 10 sets of size `r nrow(cred)/10`. They are stored in a list named test.list. At each step, the remaining part of the data base is stored in the list train.test.

```{r}
test.list <- list() # creates an empty list that will be the test sets
train.list <- list() # creates an empty list that will be the train sets
counter <- 0

# Creates the 10 sets of size 300
for (i in 1:10){
  index <- counter + c(1:100) # the row numbers that will be in the test set
  test.list[[i]] <- cred[index, ] # the test set number i
  train.list[[i]] <- cred[-index, ] # the train set number i
  counter <- counter + 100
}
```

For example, *test.list[[1]]* is a data set of 300 rows taken at random from our data.

```{r} 
# test.list[[1]] %>% kable(caption="Our first test set named test.list[[1]]") %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
#   scroll_box(width = "100%", height = "200px")
# 
# 
# train.list[[1]] %>% kable(caption="Train set associated with test.list[[1]]") %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
#   scroll_box(width = "100%", height = "200px")
```


### CART Model


```{r, chache = TRUE, results='hide'}
acc.cart.cv <- numeric(10)
for (i in 1:10){
  cart.cv <- rpart(response~., data=train.list[[i]]) # original tree
  cp.pruned <- cart.model$cptable[(min(which(cart.model$cptable[,ncol(cart.model$cptable) -1] < cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable)] + cart.model$cptable[nrow(cart.model$cptable), ncol(cart.model$cptable) - 1]))),1] # to prune at
  cart.pruned.cv <- prune(cart.model, cp=cp.pruned) # the pruned tree for predictions
  cart.pred.cv <- predict(cart.pruned.cv, newdata=test.list[[i]], type="class") # making the predictions
  tab.cart.cv <- table(test.list[[i]]$response, cart.pred.cv) # the confusion matrix
  acc.cart.cv[i] <- accuracy(tab.cart.cv) # the final accuracy
}

```

## Logistic Regression

```{r, cache = TRUE, results='hide'}
acc.glm.cv <- numeric(10)
for (i in 1:10){
  glm.cv <- glm(response ~., data=train.list[[i]], family="binomial") # original logistic regression
  logit.step.cv <- step(glm.cv, direction="both") # the pruned tree for predictions 
  glm.pred.cv <- ifelse(
  predict(logit.step.cv, newdata=test.list[[i]], type="response") > 0.5, "good", "bad"
  ) # making the predictions
  tab.glm.cv <- table(test.list[[i]]$response, glm.pred.cv) # the confusion matrix
  acc.glm.cv[i] <- accuracy(tab.glm.cv) # the final accuracy
}

```



```{r}
acc.cart.cv
mean(acc.cart.cv)
sd(acc.cart.cv)

acc.glm.cv # the vector of accuracies for the glm model
mean(acc.glm.cv) # the average accuracy
sd(acc.glm.cv) # the standard deviation of the accuracy
```


